### 2018-03-09 paper/background.tex
Address some of Neil's comments

Another distinguishing feature of \Excel is \emph{self-tracking}. Most build
systems track changes of inputs and intermediate results, executing dependent
tasks whenever they change, but \Excel can also track changes in the tasks
themselves: if a formula is modified, \Excel will recompute it and propagate
the changes. Self-tracking is uncommon in software build systems, where one
often needs to manually initiate a full rebuild even if just a single task has
changed.

@@

The last row of the table describes the new build system proposed in this paper,
which shares the advantages of \Shake and \Bazel.

\begin{table}[h]
\smaller
\centering
\begin{tabular}{l||l|c|c|c|c||l|l}
\hline
$\!\!$Build system$\!$&$\!$Dependencies$\!$&$\!$Minimal$\!$&$\!$Self-tracking$\!$&$\!$Cutoff$\!$&$\!$Cloud$\!$&$\!$Metadata$\!$&$\!$Algorithm$\!\!$\\\hline
$\!\!$\Make       $\!$&$\!$Static  & Yes & No  & No  & No  &$\!$Dirty bit       $\!$&$\!$Topological $\!\!$\\
$\!\!$\Excel      $\!$&$\!$Dynamic & No  & Yes & No  & No  &$\!$Dirty bit, chain$\!$&$\!$Chain, defer$\!\!$\\
$\!\!$\Shake      $\!$&$\!$Dynamic & Yes & No  & Yes & No  &$\!$Graph           $\!$&$\!$Recursive   $\!\!$\\
$\!\!$\Bazel      $\!$&$\!$Static  & Yes & No  & Yes & Yes &$\!$Graphs, cache   $\!$&$\!$Topological $\!\!$\\\hline
$\!\!$This paper  $\!$&$\!$Dynamic & Yes & No? & Yes & Yes &$\!$Graphs, cache   $\!$&$\!$Recursive   $\!\!$\\
\hline
\end{tabular}
\vspace{2mm}
\caption{Summary of build system differences.\label{tab-summary}}
\vspace{-7mm}
\end{table}

>>>>

Another distinguishing feature of \Excel is \emph{self-tracking}. Most build
systems track changes of inputs and intermediate results, executing dependent
tasks whenever they change, but \Excel can also track changes in the tasks
themselves: if a formula is modified, \Excel will recompute it and propagate
the changes. Self-tracking is uncommon in software build systems, where one
often needs to manually initiate a full rebuild even if just a single task has
changed. We further discuss self-tracking in~\S\ref{sec-tracking-aspects}.

@@

In this paper we show which build system properties are consequences of specific
implementation choices (metadata and algorithm), and how one can obtain new
build systems with desired properties by recombining parts of existing
implementations. As a compelling example, we demonstrate how to combine
advantages of \Shake and \Bazel in a cloud build system with dynamic dependencies.

\begin{table}[h]
\smaller
\centering
\begin{tabular}{l||l|c|c|c||l|l}
\hline
$\!\!$Build system & Dependencies & Minimal & Cutoff & Cloud & Metadata                       & Algorithm   $\!\!$\\\hline
$\!\!$\Make        & Static       & Yes     & No     & No    & File modification times        & Topological $\!\!$\\
$\!\!$\Excel       & Dynamic      & No      & No     & No    & Dirty cells, calculation chain & Chain, defer$\!\!$\\
$\!\!$\Shake       & Dynamic      & Yes     & Yes    & No    & Last dependency graph          & Recursive   $\!\!$\\
$\!\!$\Bazel       & Static       & Yes     & Yes    & Yes   & All dependency graphs, cache   & Topological $\!\!$\\\hline
\hline
\end{tabular}
\vspace{2mm}
\caption{Summary of build system differences.\label{tab-summary}}
\vspace{-7mm}
\end{table}
